### 2019-05-19 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Concentration of F_R

We seek to find \m {\d_s \SB {\M{F}_B} \SB {\o_t}}, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
Try to set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\a >0}.
They are (with a slight of abuse of meaning of \m {\o_t} and so on)
\Disp{
\NC d \o_t
=\NC \F {1} {\R {\pi} \a} \exp
  \RB {-\F{1}{\a^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC d \o_t
=\NC \F {1} {\R {\pi} \a} \exp
  \RB {-\F{1}{\a^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC n_R
= \NC 0, 1, 2, \dots, N_R -1 \NR
\NC n_Y
= \NC 0, 1, 2, \dots, N_Y -1 \NR
}
We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
\Disp{
\NC \NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
\NC =\NC \F{\R{\pi}}{2} \a \NR[+]
\NC M_2
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
\NC =\NC \a^2 \NR[+]
\NC M_4
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
\NC =\NC 2 \a^4 \NR[+]
}
Fix test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we have to study the concentration of \m {\VNm {\M{F}_B \V{u}}_2} in probability mass.
We shall exploit Chebyshev bound, which required the first and second moment to be found.
\Disp{
\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2} \NR
\NC = \NC \MB{E}
\SB {
  \sum_{n_R=0}^{N_R-1}
  \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
} \NR
\NC = \NC \sum_{n_R=0}^{N_R-1}
  \MB{E} \SB {\Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2}
\NR
\NC = \NC
\sum_{n_R=0}^{N_R-1}
  \MB{E} \SB {
     2 \sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
       \MF {Re} \SB{
         \M{F}_B \DB {n_R, n_Y} ^* \M{F}_B \DB {n_R, n_Y'}
         \V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
       }
   } \NR
\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
  \MB{E}
     \SB {\sum_{n_Y=0}^{N_Y-1} \Nm {\M{F}_B \DB {n_R, n_Y}}^2 \Nm {\V{u} \DB{n_Y}}^2}
\NR
\NC = \NC
2 \sum_{n_R=0}^{N_R-1}
\sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\MF {Re} \SB{
   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^*}
   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y'}}
}
\V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
\NR
\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
   \sum_{n_Y=0}^{N_Y-1} \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2} \Nm {\V{u} \DB{n_Y}}^2
\NR
\NC = \NC \a^2 N_R \VNm {\V{u}} _2 ^2 \NR[+]
}
Thus, we may set
\Disp{
\NC \a
=\NC \F {1} {\R{N_R}} \NR[+]
}
To make
\Disp{
\NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
=\NC \VNm {\V{u}} _2 ^2
}

Similarly, we have to find, in advance, the second moment.
\Disp{
\NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4}
=\NC \SB {
  \RB {
    \sum_{n_R=0}^{N_R-1}
    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
  } ^2
}
\NR[+]
}
Without spelling out everything, we notice that as long as a term has a single \m {\M{F}_B \DB {n_R, n_Y}} factor, it's expectation is zero.
Also notice that
\Disp{
\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
\NC \NC \quad \quad +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
\NC = \NC 0 \NR[+]
}
Having said that, with straightforward calculation, we see that the remaining terms are
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4} \NR
\NC = \NC
\sum_{n_R=0}^{N_R-1} \sum_{n_Y=0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^4
\Nm {\V{u} \DB{n_Y}} ^4 \NR
\NC \NC \quad \quad
+\sum _{\startsubstack n_R, n_R' =0 \NR n_R <n_R' \stopsubstack}^{N_R-1}
\sum _{n_Y =0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R, n_R' =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R, n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC =\NC N_R \D M_4 \D \VNm {\V{u}} _4 ^4
   +\F {1} {2} N_R \RB {N_R-1} \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \NC \quad \quad + N_R^2 \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}
   + N_R \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
}
Plugging in the moments, we have
\Disp{
\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
}
Use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, and we have simply
\Disp{
\NC \NC \leq \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}
In conclusion,
\Disp{
\NC \Ss{Var} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}
Thus, by Chebyshev bound,
\Result
{Lemma}
{
Let \m {\M{F}_B \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_Y}}, and for any \m {\e >0},
\Disp{
\NC \MB{P} _{\o_t}
\SB {
  \Nm {\VNm {\M{F}_B \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC \F {1} {2\e^2} \NR[+]
}
}

@@

Let \m {\M{F}_B \DB {n_R, n_Y}} be uniformly distributed on the unit circle on the complex plane, which gives probability density

\Disp{
\NC d \o_t
= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_R, n_Y} \SB {\o_t}}} ^2}^{-1/2}
d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC d \o_t
= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_R, n_Y} \SB {\o_t}}} ^2}^{-1/2}
d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
}

\Disp{
\NC \NC \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} \NR
\NC =\NC \a \NR[+]
\NC M_2
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
\NC =\NC \a^2 \NR[+]
\NC M_4
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
\NC =\NC \a^4 \NR[+]
}

>>>>

We seek to find \m {\d_s \SB {\M{F}_B} \SB {\o_t}}, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
Try to set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\a >0}.
They are (with a slight of abuse of meaning of \m {\o_t} and so on)
\Disp{
\NC d \o_t
=\NC \F {1} {\R {\pi} \a} \exp
  \RB {-\F{1}{\a^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC d \o_t
=\NC \F {1} {\R {\pi} \a} \exp
  \RB {-\F{1}{\a^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC n_R
= \NC 0, 1, 2, \dots, N_R -1 \NR
\NC n_Y
= \NC 0, 1, 2, \dots, N_Y -1 \NR
}
We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
\Disp{
\NC \NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
\NC =\NC \F{\R{\pi}}{2} \a \NR[+]
\NC M_2
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
\NC =\NC \a^2 \NR[+]
\NC M_4
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
\NC =\NC 2 \a^4 \NR[+]
}
Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we have to study the concentration of \m {\VNm {\M{F}_B \V{u}}_2} in probability mass.
We shall exploit Chebyshev bound, which required the first and second moment to be found.
\Disp{
\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2} \NR
\NC = \NC \MB{E}
\SB {
  \sum_{n_R=0}^{N_R-1}
  \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
} \NR
\NC = \NC \sum_{n_R=0}^{N_R-1}
  \MB{E} \SB {\Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2}
\NR
\NC = \NC
\sum_{n_R=0}^{N_R-1}
  \MB{E} \SB {
     2 \sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
       \MF {Re} \SB{
         \M{F}_B \DB {n_R, n_Y} ^* \M{F}_B \DB {n_R, n_Y'}
         \V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
       }
   } \NR
\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
  \MB{E}
     \SB {\sum_{n_Y=0}^{N_Y-1} \Nm {\M{F}_B \DB {n_R, n_Y}}^2 \Nm {\V{u} \DB{n_Y}}^2}
\NR
\NC = \NC
2 \sum_{n_R=0}^{N_R-1}
\sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\MF {Re} \SB{
   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^*}
   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y'}}
}
\V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
\NR
\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
   \sum_{n_Y=0}^{N_Y-1} \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2} \Nm {\V{u} \DB{n_Y}}^2
\NR
\NC = \NC \a^2 N_R \VNm {\V{u}} _2 ^2 \NR[+]
}
Thus, we may set
\Disp{
\NC \a
=\NC \F {1} {\R{N_R}} \NR[+]
}
To make
\Disp{
\NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
=\NC \VNm {\V{u}} _2 ^2
}

Similarly, we have to find, in advance, the second moment.
\Disp{
\NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4}
=\NC \SB {
  \RB {
    \sum_{n_R=0}^{N_R-1}
    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
  } ^2
}
\NR[+]
}
Without spelling out everything, we notice that as long as a term has a single \m {\M{F}_B \DB {n_R, n_Y}} factor, it's expectation is zero.
Also notice that
\Disp{
\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
\NC \NC \quad \quad +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
\NC = \NC 0 \NR[+]
}
Having said that, with straightforward calculation, we see that the remaining terms are
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4} \NR
\NC = \NC
\sum_{n_R=0}^{N_R-1} \sum_{n_Y=0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^4
\Nm {\V{u} \DB{n_Y}} ^4 \NR
\NC \NC \quad \quad
+\sum _{\startsubstack n_R, n_R' =0 \NR n_R <n_R' \stopsubstack}^{N_R-1}
\sum _{n_Y =0}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R, n_R' =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC \NC \quad \quad
+\sum _{n_R =0}^{N_R-1}
\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
\Nm {\M{F}_B \DB {n_R, n_Y'}} ^2
\Nm {\V{u} \DB{n_Y}} ^2
\Nm {\V{u} \DB{n_Y'}} ^2 \NR
\NC =\NC N_R \D M_4 \D \VNm {\V{u}} _4 ^4
   +\F {1} {2} N_R \RB {N_R-1} \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \NC \quad \quad + N_R^2 \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}
   + N_R \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
}
Plugging in the moments, we have
\Disp{
\NC =\NC -\F{3}{2} \RB {1 -\F{1}{N_R}} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3 +\F{1}{N_R}} \VNm {\V{u}} _2 ^4 \NR[+]
}
Use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, and we have simply
\Disp{
\NC \NC \leq \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}

In conclusion,
\Disp{
\NC \Ss{Var} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}
Thus, by Chebyshev bound,
\Result
{Lemma}
{
Let \m {\M{F}_B \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_Y}}, and for any \m {\e >0},
\Disp{
\NC \MB{P} _{\o_t}
\SB {
  \Nm {\VNm {\M{F}_B \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC \F {1} {2\e^2} \NR[+]
}
}

@@

Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
\Disp{
\NC d \o_t
= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} ^2}^{-1/2}
d \MF{Re} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
\NC d \o_t
= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} ^2}^{-1/2}
d \MF{Im} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
}
As a result,
\Disp{
\NC \NC \MB{E} _{\o_t} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}} \NR
\NC =\NC \a \NR[+]
\NC M_2
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^2} \NR
\NC =\NC \a^2 \NR[+]
\NC M_4
:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^4} \NR
\NC =\NC \a^4 \NR[+]
}

Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_H}}, 
By a similar argument, we may set
\Disp{
\NC \a
=\NC \F {1} {\R{N_H}} \NR[+]
}
to make
\Disp{
\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_R \SB {\o_t} \V{u}} _2 ^2} \NR
\NC = \NC \VNm {\V{u}} _2 ^2 \NR[+]
}
Furthermore, if we plug in the moments and use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, we have simply
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{F}_R \V{u}} _2 ^4} \NR
\NC =\NC \RB {N_H M_4 -\F{1}{2} \RB {3N_H^2 +N_H} M_2^2} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3N_H^2 +N_H} M_2^2 \VNm {\V{u}} _2 ^4 \NR
\NC =\NC -\F{1}{2} \RB {3 -\F{1}{N_H}} \VNm {\V{u}} _4 ^4
+\F{1}{2} \RB {3 +\F{1}{N_H}} \VNm {\V{u}} _2 ^4 \NR
\NC \leq \NC \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}

In conclusion,
\Disp{
\NC \Ss{Var} _{\o_t} \SB {\VNm {\M{F}_R \SB {\o_t} \V{u}} _2 ^2}
\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
}
Thus, by Chebyshev bound, we obtain an identical expression,
\Result
{Lemma}
{
Let \m {\M{F}_R \in \MB {M}_{\MB {C}} \SB {N_H, N_R}} be generated randomly according to ().
Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_R}}, and for any \m {\e >0},
\Disp{
\NC \MB{P} _{\o_t}
\SB {
  \Nm {\VNm {\M{F}_R \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC \F {1} {2\e^2} \NR[+]
}
}
